---
title: "Analyzing COVID-19 in Austin"
description: |
  **Note to readers: this is a test post!** Austin Public Heath has been profiled numerous times throughout the pandemic as being relentless in their efforts to get good data, despite multiple challenges and barriers. In this post, I take a look at local COVID data for Austin that has been collected by Austin Public Health. 
author:
  - name: Matt Worthington 
    url: https://mrworthington.com/about
    affiliation: Me, Myself, and I
    affiliation_url: https://mrworthington.com
date: 05-20-2020
creative_commons: CC BY-NC
output:
  distill::distill_article:
    css: hospital_header.css
    self_contained: false
preview: ryan-magsino-sohLeI-k-HU-unsplash.jpg
twitter:
  creator: "@mrworthington"
---

# Up Front Note!

I am currently switching my blog over to a new platform and am testing out some interactive components on the blog post.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(janitor)
library(gfonts)
library(flextable)
library(tinter)
library(geojsonsf)
library(highcharter)
library(tigris)
library(geojson)
library(sf)

options(tigris_use_cache=TRUE)

# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

```{r echo=FALSE, message=FALSE, warning=FALSE, layout="l-page", fig.height=6}
library(ggiraph)
library(tidyverse)
library(gfonts)
library(flextable)
library(tinter)
ts_county_cases <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")
sf_counties <- tidycensus::county_laea
ts_county_cases_sf <- ts_county_cases %>% 
  filter(date=="2020-03-27",
         state=="Texas") %>% 
  left_join(sf_counties, by=c("fips"="GEOID")) %>% 
  sf::st_as_sf()
# flextable part -----
fun_flextable <- function(dat){
  ft <- flextable(dat, col_keys = c("county", "cases", "deaths"), 
                  defaults = list(fontname = "Work Sans"), 
                  theme_fun = theme_vanilla)
  ft <- fontsize(ft, part = "all", size = 20)
  ft <- bold(ft, part = "header", bold = TRUE)
  ft <- color(ft, color = "black", part = "all")
  ft <- set_table_properties(ft, layout = "autofit")
  as.character(htmltools_value(ft))
}
temp_dat <- as.data.frame(ts_county_cases_sf)[,c("county", "cases", "deaths")]
temp_dat <- split(temp_dat, seq_len(nrow(temp_dat)))
ts_county_cases_sf$tooltip <- map_chr(temp_dat, fun_flextable)
# end of flextable part
tx_map <- ts_county_cases_sf %>%
  ggplot() +
  geom_sf(data=sf_counties %>% filter(str_detect(GEOID,"48")),color="#dddddd", fill="#f2f2f2", lwd=.3) +
  geom_sf_interactive(aes(fill=cases, tooltip=tooltip, data_id = county), lwd=.3) +
  scale_fill_gradientn(colours = tinter("#5da5da", steps = 5), labels = function(x) paste0(x,"Cases")) +
  coord_sf(datum=NA) +
  hrbrthemes::theme_ipsum_es(base_family="Work Sans") +
  theme(plot.title = element_text(family="Work Sans", face = "bold"),
        plot.subtitle = element_text(family="Work Sans", face = "plain"),
        plot.caption = element_text(family="Work Sans", face = "plain")) + 
  labs(title="Confirmed COVID-19 Cases By County - Texas",
       subtitle="As of March 26th, 2020",
       caption="SOURCE: New York Times COVID-19 Database")
girafe(ggobj = tx_map, fonts = list(sans = "Work Sans"), width_svg = 12, height_svg = 8,
       options = list(
         opts_tooltip(css = "padding:5px;background:white;border-radius:2px 2px 2px 2px;"),
         opts_hover_inv(css = "opacity:0.8;"),
         opts_hover(css = "stroke-width:2;")
       ))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, layout="l-page", fig.height=6}

library(tidyverse)
library(janitor)
library(gfonts)
library(ggiraph)
library(flextable)
library(tinter)
# library(geojsonsf)
# library(highcharter)
library(tigris)
# library(geojson)
library(sf)

tx_zips <- tigris::zctas(state="TX",cb=TRUE) 

sf_counties <- tigris::counties(state="TX") %>% filter(GEOID=="48453")

# For ArcGIS Data, The service ID is the key that goes after the datasets directory. Then use the 'ID' provided to pull the data into whatever format you want. For ATX, visit this site: https://services.arcgis.com/0L95CJ0VTaxqcmED/ArcGIS/rest/services/web0723/FeatureServer

atx_covid_zips_cases <- readr::read_csv("https://opendata.arcgis.com/datasets/4d913cdf3d894c3898696a7216e44180_02.csv") %>% 
  janitor::clean_names() %>% 
  dplyr::mutate(zipcode=as.character(zipcode))

atx_zips_by_cases_sf <- atx_covid_zips_cases %>%
  dplyr::left_join(tx_zips, by=c("zipcode"="GEOID10")) %>% 
  dplyr::select(zipcode, count, geometry) %>% 
  sf::st_as_sf() %>% 
  st_transform(crs="ESRI:102339")

# flextable part -----
fun_flextable <- function(dat){
  ft <- flextable(dat, col_keys = c("zipcode", "count"), 
                  defaults = list(fontname = "Roboto"), 
                  theme_fun = theme_vanilla)
  ft <- fontsize(ft, part = "all", size = 20)
  ft <- bold(ft, part = "header", bold = TRUE)
  ft <- color(ft, color = "black", part = "all")
  ft <- set_table_properties(ft, layout = "autofit")
  as.character(htmltools_value(ft))
}
temp_dat <- as.data.frame(atx_zips_by_cases_sf)[,c("zipcode", "count")]
temp_dat <- split(temp_dat, seq_len(nrow(temp_dat)))
atx_zips_by_cases_sf$tooltip <- map_chr(temp_dat, fun_flextable)
# end of flextable part

tx_map <- atx_zips_by_cases_sf %>%
  ggplot() +
  geom_sf_interactive(aes(fill=count, tooltip=tooltip, data_id = zipcode), color="#6d6d6d", lwd=.3) +
  geom_sf(data=sf_counties, color="#1d1d1d", fill=NA, lwd=1) +
  scale_fill_gradientn(colours = tinter("#5da5da", steps = 5), labels = function(x) paste0(x,"Cases")) +
  coord_sf(datum=NA) +
  hrbrthemes::theme_ipsum_es(base_family="Roboto") +
  theme(plot.title = element_text(family="Roboto", face = "bold"),
        plot.subtitle = element_text(family="Roboto", face = "plain"),
        plot.caption = element_text(family="Roboto", face = "plain")) + 
  labs(title="Confirmed COVID-19 Cases In Austin, TX",
       subtitle="As of July 29th, 2020",
       caption="SOURCE: Austin Public Health")

girafe(ggobj = tx_map, fonts = list(sans = "Roboto"), width_svg = 12, height_svg = 8,
       options = list(
         opts_tooltip(css = "padding:5px;background:white;border-radius:2px 2px 2px 2px;"),
         opts_hover_inv(css = "opacity:0.8;"),
         opts_hover(css = "stroke-width:2;")
       ))



```

```{r echo=FALSE, message=FALSE, warning=FALSE, layout="l-page"}
library(highcharter)
library(vroom)
library(lubridate)
library(janitor)
tx2036_hc <- hc_theme_merge(
  hc_theme_smpl(),
  hc_theme(chart = list(backgroundColor = "#fff", 
                        style = list(fontFamily = 'Roboto', 
                                     fontSize = "28px",  fontWeight = "bold",
                                     color="#4d4d4d", textTransform="initial")),
           title = list(style = list(fontFamily = 'Roboto', 
                                     fontWeight="bold",
                                     color="#2d2d2d"),
                        align = "left"), 
           subtitle = list(style = list(fontFamily = 'Roboto',
                                        color="#7d7d7d",
                                        textTransform="initial",
                                        fontWeight="400",
                                        fontSize = "14px"),
                           align = "left"), 
           legend = list(align = "right", 
                         style = list(fontFamily = 'Roboto', color="#6d6d6d"),
                         itemStyle = list(fontFamily = 'Roboto', color = '#6d6d6d'),
                         itemHoverStyle = list(color = 'gray'),   
                         verticalAlign = "top"),
           credits = list(style = list(color = "#fff")),
           xAxis = list(labels =list(style = list(fontFamily = 'Roboto', color="#2d2d2d")), 
                        title = list(style = list(color = "#4d4d4d", fontSize = "12px", 
                                                  color="#4d4d4d",fontWeight="500")),
                        gridLineWidth = 0,
                        gridLineColor = "#9d9d9d", 
                        lineColor = 'rgba(0,0,0,0.7)', 
                        minorGridLineColor = 'rgba(0,0,0,0.7)', 
                        tickColor = "#9d9d9d", 
                        tickWidth = 1), 
           yAxis = list(labels =list(style = list(fontFamily = 'Roboto', color="#2d2d2d")), 
                        title = list(style = list(color = "#fff", fontSize = "12px", 
                                                  color="#fff",fontWeight="500")), 
                        gridLineWidth = .5,
                        gridLineColor = 'rgba(0,0,0,0.15)', 
                        lineColor = 'rgba(0,0,0,0.15)', 
                        minorGridLineColor = 'rgba(0,0,0,0.15)', 
                        tickColor = "#9d9d9d", 
                        tickWidth = 2)))

key_events <- vroom("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ2q_c5RpywszCamM3VINgAwZ51OJoPfBFflEvXpuAqAZrw9SDovcGnfDOlF7uwzCnZf5XMkEluhlUb/pub?output=csv") %>% 
  clean_names() %>% 
  mutate(date=as_date(date))

r_naught <- vroom("https://d14wlfuexuxgcm.cloudfront.net/covid/rt.csv") %>% 
  filter(region=="TX")

 key_events_fltr <- key_events %>%
      filter(!str_detect(event,"Stimulus"))
    
    dates <- key_events_fltr$date
    events <- key_events_fltr$event
    
    plotLines <- map2(key_events_fltr$date,key_events_fltr$event,
                      ~list(label = list(text = .y,
                                         style = list(color = "rgba(0, 0, 0, 0.6)", 
                                                      fontSize='12px',textTransform='initial')),
                            color = "rgba(0, 0, 0, 0.6)",
                            width = 1,
                            dashStyle = "Dash",
                            value = datetime_to_timestamp(as.Date(.x, tz="UTC"))))
    
   myMenuItems <- c("downloadPNG", "downloadJPEG", "downloadPDF", "downloadCSV" )
    
   r_naught %>% 
      hchart("line", hcaes(x = date, y = mean), animation=FALSE,
             tooltip = FALSE,
             threshold = 1, color = "#F26852", negativeColor = "#FFD100") %>%
      hc_add_series(r_naught, type = "arearange",
                    hcaes(x = date, low = lower_80,
                          high = upper_80),
                    threshold = 1, color = "#F26852", negativeColor = "#FFD100",
                    linkedTo = "r_naught") %>%
      hc_plotOptions(arearange = list(fillOpacity=.3)) %>%
      hc_title(
        text ="Texas Effective Reproduction Rate · R<sub>t</sub>",
        useHTML = TRUE) %>% 
      hc_subtitle(
        text ="From R<sub>t</sub> Live: R<sub>t</sub>  is the average number of people who become infected by an infectious person.</br></br><span style='color: #F26852'>If it’s above 1.0, COVID-19 will spread quickly.</span> <span style='color: #FFD100'>If it’s below 1.0, infections will slow.</span>",
        useHTML = TRUE) %>%
      hc_yAxis(title = list(text="Effective Reproduction Rate (R<sub>t</sub>)"),
               min = min(r_naught$lower_80), 
               max = max(r_naught$upper_80)) %>% 
      hc_xAxis(title=NULL,
               plotLines = plotLines) %>% 
      hc_tooltip(table = FALSE, sort = FALSE,
                 pointFormat = "Effective Reproduction Rate · R<sub>t</sub>: {point.mean:,.2f}<br>") %>% 
      hc_credits(
        enabled = TRUE,
        text = "Source: rt.live Analysis",
        href = "https://rt.live") %>%
      hc_add_theme(tx2036_hc)  %>% 
      hc_size(height = NULL, width = 800) %>%
        hc_exporting(enabled=TRUE, scale=2, sourceWidth= 1200, sourceHeight = 600, 
                     allowHTML = TRUE,
                     buttons = list(contextButton = list(menuItems = myMenuItems, 
                                                         title = "Export This Chart",
                                                         symbol = 'menuball', 
                                                         symbolStrokeWidth = 1,
                                                         symbolFill = 'rgba(93,165,218, 0.9)',
                                                         symbolStroke ='#4d4d4d',
                                                         theme = list(fill='#ffffff'))),
                     chartOptions = list(title =  list(style = list(fontWeight = '800', fontSize = '22px')),
                                         subtitle =  list(style = list(fontSize = '14px'))))
   
   
    
```


## Acknowledgments {.appendix}

This is a place to recognize people and institutions. It may also be a good place
to acknowledge and cite software that makes your work possible.

## Author Contributions {.appendix}

We strongly encourage you to include an author contributions statement briefly 
describing what each author did.

